Optimizing the power of adaptive seamless designs using Bayesian Optimization

### 2020-09-28 main.tex
stupid tikz

% own packages
\usepackage{siunitx}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{assets/friede_refinement_2010_fig2.png}
\caption{Application of the refined clinical scenario evaluation framework to adaptive seamless designs in progressive multiple sclerosis. REPLACE WITH TikZ}
\label{fig:friede_refinement_2010_fig2}
\end{figure}
%FIXME Is this the right paper? Convert to tikz! Tim schickt mir das Original!
%Friede et al (2010) DIJ, Figure 2 https://link.springer.com/content/pdf/10.1177/009286151004400507.pdf? https://link.springer.com/content/pdf/10.1177/009286151004400607.pdf

>>>>

% own packages
\usepackage{siunitx}
\usepackage{enumitem}
% tikz
\usepackage{tikz}
% we want ER + above/below + left/right
\usetikzlibrary{er,arrows, chains, fit, positioning, calc, shapes}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{assets/friede_refinement_2010_fig2.png}
\caption{Application of the refined clinical scenario evaluation framework to adaptive seamless designs in progressive multiple sclerosis. REPLACE WITH TikZ}
\label{fig:friede_refinement_2010_fig2}
\end{figure}

\tikzset{nearnodes/.style={draw, node distance=0cm,}}
\begin{tikzpicture}[auto,node distance=0.3cm,align=center,text width = 3cm, font=\scriptsize]
  \node[draw, ellipse, minimum height=1cm, text width=3cm] (ClinicalScenarios) at (0,0) {
    \textbf{Clinical scenarios}\\
    Simulation Studies};
  \node[name=block, rectangle split, rectangle split parts=2, nearnodes, above left = of ClinicalScenarios] (HistoricalDataPoints)
  { \begin{itemize}[leftmargin=.3cm]
      \item Correlation between early interim and late disability outcomes.
    \end{itemize}
    \nodepart{second} Combination of options
  };
  \node[name=block, rectangle split, rectangle split parts=2, nearnodes, left = of HistoricalDataPoints] (UnknownPoints)
  { \begin{itemize}[leftmargin=.3cm]
      \item Treatment effect on early interim outcome.
      \item Treatment effect on late disability outcome
    \end{itemize}
    \nodepart{second} Constrained by health care environment/infrastructure
  };
  %\node[nearnodes, inner xsep=1em, inner ysep=1em, above left = of ClinicalScenarios, fit = (HistoricalDataPoints) (UnknownPoints)] (boxDiseaseSpecific) {};
  \node[draw, above = of HistoricalDataPoints, text width = 6cm] (DiseaseSpecific) {\textbf{Disease-specific features}};
  %\node[draw, above right = of ClinicalScenarios] (DesignOptions) {Design options};
  \node[name=block, rectangle split, rectangle split parts=2, nearnodes, above right = of ClinicalScenarios] (CombinationPoints)
  { \begin{itemize}[leftmargin=.3cm]
      \item Adaptive seamless design time point of interim analysis
      \item Treatment selection rules at interim Conventional phase 2/3
      \item split of resources between phases
      \item end oh phase futility criteria
    \end{itemize}
    \nodepart{second} Combination of options
  };
  \node[name=block, rectangle split, rectangle split parts=2, nearnodes, left = of CombinationPoints] (ConstrainedPoints)
  { \begin{itemize}[leftmargin=.3cm]
      \item Number of test treatments
      \item Total subjects in trial
      \item recruitment rate
    \end{itemize}
    \nodepart{second} Constrained by health care environment/infrastructure
  };
  \node[draw, above = of ConstrainedPoints,text width = 6cm] (DesignOptions) {\textbf{Disease-specific features}};
  \node[draw, below = of ClinicalScenarios] (DesignPerformance) {
    \textbf{Design performance} \\ e.g.\ statistical power};
  \node[draw, right = of DesignPerformance] (Evaluation) {
    \textbf{Clinical Scenario Evaluation}\\
    Design performance measures evaluated across a wide range of clinical scenarios};
  \draw[->] (HistoricalDataPoints) -- (ClinicalScenarios);
  \draw[->] (UnknownPoints) -- (ClinicalScenarios);
  \draw[->] (CombinationPoints) -- (ClinicalScenarios);
  \draw[->] (ConstrainedPoints) -- (ClinicalScenarios);
  \draw[->] (ClinicalScenarios) -- (DesignPerformance);
  \draw[->] (DesignPerformance) -- (Evaluation);
\end{tikzpicture}
%FIXME Is this the right paper? Convert to tikz! Tim schickt mir das Original!
%Friede et al (2010) DIJ, Figure 2 https://link.springer.com/content/pdf/10.1177/009286151004400507.pdf? https://link.springer.com/content/pdf/10.1177/009286151004400607.pdf
